Behind Bars and Beyond: Investigating Socioeconomic Drivers of Incarceration Rates in the United States

### 2024-04-17 paper/paper.qmd
Began data section
Began data section by adding some background information

>>>>

This paper utilizes 5 datasets, all provided by the World Population Review and each providing information on one of the 5 factors involved in this study. @sec-incarceration-data features the most recently available information on incarcerations and incarceration rates of 219 countries and territories as of 2024. @sec-poverty-data features the data on the poverty rates of 164 nations. @sec-crime-data

## Incarceration Rate Dataset {#sec-incarceration-data}

## Poverty Rate Dataset {#sec-poverty-data}

## Crime Rate Dataset {#sec-crime-data}

## Unemployment Rate Dataset {#sec-unemployment-data}

## Education Ranking Dataset {#sec-education-data}
